WTCIII-Figures

### 2015-07-01 markdown/WTC3_figures.Rmd
fixing plots for manuscript
major changes in legends

changed colors

started aci model plot

```{r par, fig.width=8, fig.height=6}
source("master_scripts/par.R")
```  
Figure 1. Local light environment for sun and shade leaves for each gas exchange campaign. Means and standard errors represent 1m integrated PPFD (n=5), measured with a ceptometer, at the canopy height of each selected leaf.

![aci](aci_curves.png)
Figure2. Predicted photosynthetic CO~2~ response (ACi) curves for sun and shade leaves at elevated and ambient temperature treatments. ACi curves were developed at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^). ACi curves were taken once on well watered trees before the initiation of the drought treatment.

```{r, results='asis'}
aci_leaf <- read.csv("calculated_data/tdl_aci.csv")
names(aci_leaf) <-c("Leaf", "Temperature", "Vcmax", "Jmax", "Vcmax_se", "Jmax_se")

aci_leaf2 <- aci_leaf[,c(1,2,3,5,4,6)]

panderOptions("digits", 3)
pander(aci_leaf2, caption = "Table 1.  Biochemical parameters estimated from ACi curves above")
```

```{r wateruse, fig.width=8, fig.height=10}
source("master_scripts/wateruse.R")
```  
Figure 3. Response of instantaneous water use efficiency (ITE) to leaf vapor pressure deficit (VPD) (a) and response of leaf photosynthesis rates to stomatal conductance (b) for sun and shade leaves at elevated and ambient temperature treatments. For (a)  lines represent predictions from the optimal ITE model with k=0.05 and a specific g1 value for each leaf type and treatment. For (b) dashed lines represent 95% confidence intervals from a general additive model with k=5.

```{r c13n, fig.width=8, fig.height=6}
source("master_scripts/c13_Narea.R")
```  
Figure 4. The relationship between leaf  $\delta$^13^C and nitrogen~area~ for sun and shade leaves at elevated and ambient temperature treatments.

```{r gm, fig.width=8, fig.height=10}
source("master_scripts/gm_figures.R")
```  
Figure 5. Response of mesophyll conductance to leaf temperature (a) and the response of leaf photosynthesis to mesophyll conductance (b) for sun and shade leaves at elevated and ambient temperature treatments.  The mean difference in mesophyll conductance (c) and photosynthesis (d) between sun and shade leaves with standard errors.  For (a) and (b) lines represent 95% confidence intervals generated with bootstrapping methods (n=999) from mixed effect linear model equations with chamber as a random effect.

```{r lights, fig.width=8, fig.height=10}
source("master_scripts/gm_lightson.R")
```  
Figure 6. Response of photosynthesis to mesophyll conductance following a maximum sunfleck response of shade leaves (a) and overall mean values of mesophyll conductance (c) and photosynthesis (d) to sun flecks in shade leaves with standard errors.  The sunfleck was simulated by increasing the PPFD to the level of the sun leaf in the same chamber. The response of leaf physiology to sun flecks was recorded once both photosynthesis and stomatal conductance were stable in the gas exchange leaf cuvette (ca. 25min).

>>>>

#### <u>Figures</u>
```{r par, fig.width=8, fig.height=6}
source("master_scripts/par.R")
```  
Figure 1. Local light environment for sun and shade leaves for each gas exchange campaign. Means and standard errors represent 1m integrated PPFD (n=5), measured with a ceptometer, at the canopy height of each selected leaf.

```{r acicurves, fig.width=8, fig.height=6}
source("master_scripts/aci_vcmaxnitro.R")
```  
Figure2. Predicted photosynthetic CO~2~ response (ACi) curves for sun and shade leaves at elevated and ambient temperature treatments. ACi curves were developed at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^)(a). The relationship between Vc~max~  and leaf nitrogen, on an area basis, for sun and shade leaves at elevated and ambient temperature treatments (b). ACi curves were taken once on well watered trees before the initiation of the drought treatment.

```{r wateruse, fig.width=8, fig.height=10}
source("master_scripts/wateruse.R")
```  
Figure 3. Response of instantaneous water use efficiency (ITE) to leaf vapor pressure deficit (VPD) for sun leaves and shade leaves at both low and high light (a) and the relationship between leaf $\delta$^13^C and leaf nitrogen~area~ for sun and shade leaves at elevated and ambient temperature treatments. For (a) VPD is the leaf to air pressure difference inside the gas exchange cuvette and lines represent predictions from the optimal ITE model with a g1 value for each leaf type and treatment.

```{r gmgs, fig.width=8, fig.height=10}
source("master_scripts/gmgs")
```  
Figure 4. The response of leaf photosynthesis rates to stomatal conductance (a) and mesophyll conductance (b) for sun leaves and shade leaves at both low and high light with elevated and ambient temperature treatments.  Dashed lines represent 95% confidence intervals from a general additive model with a smoothing factor of 5.  The response of shade leaf physiology to high light was recorded once both photosynthesis and stomatal conductance were stable in the gas exchange leaf cuvette (ca. 25min).

```{r cicc, fig.width=12, fig.height=8}
source("master_scripts/cicc_bar.R")
```  
Figure 5. The average intercellular CO~2~ concentraion (a), CO~2~ concentration in the chloroplasts (b) and CO~2~ drawdown from substomatal cavities to sites of carboxylation of sun leaves and shade leaves at both low and hight light with standard errors.

```{r barplots, fig.width=12, fig.height=6}
source("master_scripts/physiology_barplots.R")
```  
The average stomatal conductance (a), mesophyll conductance (b) and photosynthesis (c) between sun leavse and  shade leaves at both low and high light with standard errors.

```{r acimod, fig.width=12, fig.height=6}
source("master_scripts/aci_acc_model.R")
```  
The average stomatal conductance (a), mesophyll conductance (b) and photosynthesis (c) between sun leavse and  shade leaves at both low and high light with standard errors

#### <u>Supplementary Figures</u>
```{r gmparN, fig.width=8, fig.height=10}
source("master_scripts/gm_par_nitro.R")
``` 
Figure S1. The relationship between mesophyll conductance, leaf PPFD and leaf nitrogen.

```{r gmT, fig.width=8, fig.height=10}
source("master_scripts/gm_temp.R")
``` 
Figure S2. Response of mesophyll conductance to leaf temperature  for sun and shade leaves at elevated and ambient temperature treatments. For (a) and (b) lines represent 95% confidence intervals generated with bootstrapping methods (n=999) from mixed effect linear model equations with chamber as a random effect.
